Physical Characteristics Required of a Millisecond Pulsar Population to Reproduce the Galactic Center Excess

### 2021-07-08 paper/draft.tex
NPTF smoothed results

    \begin{subtable}[h]{\textwidth}
        \centering
        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
            Power law & 5.35 & 0.0448 & $\num{5.91e6}$ \\
            Log normal, GCL & 79.9 & 0.683 & 473 \\
            Log normal, GCE & 13.5 & 0.0649 & $\num{1.90e4}$ \\
            Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
            NFW NPTF & 0 & 0 & $\num{0}$ \\
            DISK NPTF & 0 & 0 & $\num{0}$ \\
            \hline
        \end{tabular}
        \caption{Smoothed sensitivity model}
        \label{tab:smoothed-results}
    \end{subtable}
    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE. For definitions of the parameterizations, see section \ref{sec:lum-funcs}.}
    \label{tab:specific-results}
\end{table}

>>>>

    \begin{subtable}[h]{\textwidth}
        \centering
        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
            Power law & 5.35 & 0.0448 & $\num{5.91e6}$ \\
            Log normal, GCL & 79.9 & 0.683 & 473 \\
            Log normal, GCE & 13.5 & 0.0649 & $\num{1.90e4}$ \\
            Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
            NFW NPTF & 2.31 & 0.0119 & $\num{1.97e3}$ \\
            DISK NPTF & 34.3 & 0.521 & $\num{-47.6}$ \\
            \hline
        \end{tabular}
        \caption{Smoothed sensitivity model}
        \label{tab:smoothed-results}
    \end{subtable}
    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE. For definitions of the parameterizations, see section \ref{sec:lum-funcs}.}
    \label{tab:specific-results}
\end{table}
